
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
	{#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
	\item\small{
    	{#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
  	\textbf{#1} & \textbf{\small #2} \\
  	\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  	\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
  	\small#1 & \textbf{\small #4}\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
	{\Huge \scshape Omkar Geedh} \\ \vspace{1pt}
	Mumbai, Maharashtra \\ \vspace{1pt}
	\small \raisebox{-0.1\height}\faPhone\ +91 7506770678 ~ \href{mailto:omkar.geedh01@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{omkar.geedh01@gmail.com}} ~
	\href{https://www.linkedin.com/in/omkar-geedh/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/omkar-geedh}}
	\vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
	\resumeSubheading
  	{Lokmanya Tilak College of Engineering, Navi Mumbai}{August 2021 - May 2024}
  	{B.E. Computer Science and Engineering (IoT, Cyber Security incld. Blockchain Technology)}{CGPA of 7.2}
   \resumeSubheading
  	{Vidyalankar Polytechnic, Mumbai}{August 2017 - June 2021}
  	{Diploma in Computer Engineering}{Passed with 90\%}

   
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
  	{Tata Institute of Fundamental Research (TIFR), Mumbai }{May 2019 -- July 2019}
  	{Software Development Engineer Intern}{Mumbai, India (on site)}
  	\resumeItemListStart
    	\resumeItem{I developed both the backend and frontend of an online student reimbursement form specifically designed for TIFR (Tata Institute of Fundamental Research), enhancing the institution's efficiency in processing reimbursement requests.}
    	
	\resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
	\vspace{-5pt}
	\resumeSubHeadingListStart
	\resumeProjectHeading
      	{\textbf{Video Streaming Website} $|$ \emph{MongoDB, ExpressJS, ReactJS, NodeJS, Firebase} }      
       \resumeItemListStart
        	\resumeItem{This platform is designed for video streaming, allowing users to watch videos, express preferences through likes or dislikes, comment on videos, and subscribe to channels.}
        	\resumeItem{The application utilizes MongoDB for database management, Firebase to store video and image assets, and a technology stack featuring Node.js with Express.js for the backend, complemented by React.js for the frontend interface.}
      	\resumeItemListEnd
	\vspace{-13pt}
  	\resumeProjectHeading
      	{\textbf{Food Delivery App} $|$ \emph{React Native, Firebase, Razorpay, NodeJS}} 
      	\resumeItemListStart
        	\resumeItem{This app is designed for a food delivery app, allowing users to order food from their favourite nearby restaurants.}
                \resumeItem{The application utilizes Firebase to store images and authenticate users, leveraging a technology stack featuring React Native to run the app natively on platforms like Android and iOS. Razorpay is integrated for handling payments within the application.}
      	\resumeItemListEnd
	\resumeSubHeadingListEnd
\vspace{0pt}

%
%-----------Achievements-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\resumeItemListStart
    	\resumeItem{Participated in the Smart India Hackathon 2023 and was selected at the institute level.}
    	\resumeItem{Achieved 1st place in the CSESA, LTCE 2023 Hackathon where more than 300 participated. }
    	\resumeItem{Selected for Aviskar 2023 hosted by Mumbai University.}
    	\resumeItem{Solved more than 100+ problems across platforms.}
    	 }
  	\resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}
 
 %
%-----------Profile Links-----------
\section{Profile Links}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\resumeItemListStart
    	\resumeItem {\href{https://www.linkedin.com/in/omkar-geedh/}{LinkedIn}}
    	\resumeItem {\href{https://github.com/OmkarGeedh}{GitHub}}
    	\resumeItem {\href{https://leetcode.com/u/OmkarGeedh/}{Leetcode}}
            \resumeItem{\href{https://omkargeedh.github.io}{Portfolio}}
    	
  	\resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
 	\textbf{Languages}{: C++, Java, HTML/CSS, JavaScript, SQL, Python} \\
 	\textbf{Technologies/Frameworks/Libraries}{: ReactJS, MongoDB, NodeJS, React Native} \\
        \textbf{Relevant Course work}{: Data Structures and Algorithms, Blockchain, Cyber Security, Machine Learning}
  \\
	}}
 \end{itemize}
 \vspace{-16pt}

\end{document}


